---
title: "30-feature-engineering"
output: html_notebook
---

## Introduction
In this part, I will write two functions which add engineered features to the dataset, including a description and rationale. Include a test to determine whether the features are working as intended.

Also, I will describe the detail another two functions to help my teammate to better create the function.

## Feature engineering already built

### Feature Engineering: month, hour of a day

I guess different months could be related to solar radiation. So I need to generate a new feature named month. Similarly, different hours of a day may also be related to radition

```{r new feature: month, hour of a day}
generate_month <- function(df, date){
df <- df %>% 
  mutate(month = factor(month({{date}}),labels = c("SEPT","OCT","NOV","DEC")),
         hour_of_day = hour({{date}}))

}

solarprediction %>% generate_month(date_time) %>% 
  assert(within_bounds(0,23), hour_of_day) %>% 
  assert(in_set(c("SEPT","OCT","NOV","DEC"), month))
```

I also use assert for 'month' and 'hour_of_day' columns to make sure the features I generate are what I want.

### Feature Engineering: day_with_sun

I believe radiation is related whether it is a day with sun or a night without sun. Therefore, I will create a new column named day_with_sun and use "TRUE" and "FALSE" to represent the judegemnt of day and night.
```{r new feature: day_with_sun}
day_with_sun <- function(df, sunset, sunrise, real_time){
  df <- df %>% 
    mutate(day_with_sun = if_else({{real_time}} >= {{sunrise}} & {{real_time}} <= {{sunset}}, "TRUE", "FALSE"))
}


solarprediction %>%
  day_with_sun(time_sun_set, time_sun_rise, time) %>% 
  assert(in_set(c("TRUE","FALSE"), day_with_sun))
```

Also, I use assert to ensure the new feature I created is what I expect.

## Feature engineering needed to be built
### Sunshine hours

The feature I would like to create is sunshine_hours. The sunshine hours = time of sun set - tine of sun rise.

What I need is how many hours. However, time_sun_rise and time_sun_set is in 'hms' format. Therefore, it requires lubridate package. **hour** and **minute** function could be used to extract hours and minutes and seperately calculate them. Finally, you just need to transfer minutes into hours and combine them together.

feature: sunshine_hours

column used: time_sun_rise, time_sun_set

key function maybe used: hour(), minute()

```{r, add_sunshine_hours}
# Add by Baiyu Chen for closing issue 1
generate_sunshine_hours <- function(df, sunset, sunrise) {
  df <- df %>% 
    mutate(sunshine_hours = 
             (hour({{sunset}}) - hour({{sunrise}})) +
             (minute({{sunset}}) - minute({{sunrise}})) / 60
          )
}
```

```{r, test_sunshine_hours}
# Add by Baiyu Chen for closing issue 1
solarprediction %>%
  generate_sunshine_hours(time_sun_set, time_sun_rise) %>% 
  assert(within_bounds(0,24), sunshine_hours)
  
```


### Compass Wind Directions

Also, I would like to modify wind_direction_degrees. 

It is in numeric formats but it should not be considered as a continious numeric variable affecting solar radiation because 355 degree is more close to 5 degree. But what if I use compass wind directions to represent wind direction degrees.

I would like to use 16 compass wind directions: "N","NNE","NE","ENE","E","ESE","SE","SSE","S","SSW","SW","WSW","W","WNW","NW","NNW". Therefore 360 degress should be evenly divided into 16 parts.

I believe case_when function could be used to build this feature. Also, a more easier way is to use factor() function. 

feature: compass_directions

column used: wind_direction_degrees

key function maybe used: case_when() / factor()