---
title: "40-prepare-modeling"
output: html_notebook
---

## Applying feature engineering functions to generate new data table
```{r applying feature engineering functions}
solar_feature_engineering <- solarprediction %>% 
  generate_month(date_time) %>% 
  #sunshine_hours(time_sun_set,time_sun_rise) %>% 
  day_with_sun(time_sun_set, time_sun_rise, time) %>% 
  #compass_directions()

head(solar_feature_engineering)
```


## Select response and predicto variables

```{r select response and predictor variables for modeling}
solar_model <- solar_feature_engineering %>% 
  select(everything(),-time, -date_time,-time_sun_rise, -time_sun_set,-wind_direction_degrees)

head(solar_model)
```

## Seperate the data set into training, validation and test set 
```{r prepare train, validation and test set for modeling}
set.seed(11)
train_sub <- sample(nrow(solar_model),0.7*nrow(solar_model))
train_set <- solar_model[train_sub,]
val_test_set <- solar_model[-train_sub,]
val_sub <- sample(nrow(val_test_set), 0.5*nrow(val_test_set))
val_set <- val_test_set[val_sub,]
test_set <- val_test_set[-val_sub,]